Lens Modeling in \sw

### 2014-06-18 text/partA.tex
a mess

Modelling with \spl involves three stages, markup of the image,
followed by intensive numerics in the background, followed by review
of diagnostics and possible discussion.  We now describe each of
these, at a conceptual level, without implementation details.

@@

The first modeling step with \spl is for the user to call up the \sw
of interest, and make an educated guess for the topography of the
arrival-time surface --- specifically, the locations of the maxima,
minima and saddle points that correspond to images of the brightest
part of the source.  Input is given by tracing a proposal for the
saddle-point contours.  Examples appear in Figures \ref{fig:6941} to
\ref{fig:7022} below (upper-left panel in each case).

@@

The exact placement of the pink spaghetti loops shown in
\Figref{input-spag} has no significance.  Their utility is
just to help mark up the image as maximum, minima and saddle points.
As the figure suggests, the marking up can be done very easily with a
mouse.  Human intuition is required to (a)~identify lensed images and
separate them from other background light sources, and (b)~classify
and order images according to arrival time.  But the computer helps by
allowing only valid lensing configurations to be entered, and ensuring
that the odd image theorem is taken care of.

>>>>

Modelling with \spl involves three stages, markup of the image,
followed by intensive numerics in the background, followed by review
of diagnostics and possible discussion.  We now describe each of
these, but do not go into implementation details.

@@

One begins by going to the \spl page and entering the number of a \sw
image tile.  \spl then presents it, along with zoom and pan options
and a markup tool.  The human modeller then has to make an educated
guess for the topography of the arrival-time surface, and input the
locations time-ordering of the maxima, minima, and saddle-points.  The
markup tool allows this information to be entered without the user
having to think explicitly about image parities or time ordering, by
tracing saddle-point contours (which the collaboration soon named
``spaghetti'', leading to the name of the program).

Examples appear in the upper-left panels of Figures \ref{fig:6941} to
\ref{fig:7022}.

  It
also allows only valid lensing configurations to be entered, including

ensuring that the odd image theorem is taken care of.

1986ApJ...310..568B

The modeller begins by going to the \spl page, and entering the \sw name

The modeller proceeds by modeling step with \spl is for the user to call up the \sw
of interest, and make an educated guess for the topography of the
arrival-time surface, specifically, the locations of the maxima,
minima and saddle points that correspond to images of the brightest
part of the source.  Input is given by tracing a proposal for the
saddle-point contours.

@@

The exact placement of the pink spaghetti loops shown in
\Figref{input-spag} has no significance.  Their utility is
just to help mark up the image as maximum, minima and saddle points.
As the figure suggests, the marking up can be done very easily with a
mouse.  Human intuition is required to (a)~identify lensed images and
separate them from other background light sources, and (b)~classify
and order images according to arrival time.
